Multitasking Interfaces on Touchscreen Mobile Devices

### 2015-12-09 sigchi-latex-proceedings 2/final-paper.tex
Small Edits
Add abstract

%\author{
%    Kyra Assaad, Zach Munro-Cape, Ajit Pawar, Ishan Thukral, \& Colin White\\
%  \sharedaffiliation
%      \affaddr{Department Computer Science }  \\
%      \affaddr{University of Toronto }   \\
%      \affaddr{Toronto, Ontario} \\
%      \email{\{kyra.assaad,zach.munro.cape,ajit.pawar,ishan.thukral,colin.white\}@mail.utoronto.ca }
%}

@@

\section{Abstract}

@@

A stacked interface may only provide nominal speed and accuracy increases when compared to a non-stacked interface. As a result, future research should focus on alternate means to facilitate app switching as opposed to the conventional chronological list of applications. Throughout all mobile multitasking interfaces, almost exclusively, the ?most recently used? rule is used to display applications in the list. Future research could look into using different sorting schemes to predict which application a user will need next. Perhaps machine learning could be applied to predict what application may be used next as is being tested in Apple?s new recents menu.

>>>>

%\author{
%    Kyra Assaad, Zach Munro-Cape, Ajit Pawar, Ishan Thukral, \& Colin White\\
%  \sharedaffiliation
%      \affaddr{Department Computer Science }  \\
%      \affaddr{University of Toronto }   \\
%      \affaddr{Toronto, Ontario} \\
%      \email{\{kyra.assaad, zach.munro.cape, ajit.pawar, ishan.thukral, colin.white\}@mail.utoronto.ca }
%}

@@

\section{Abstract}
Mobile smartphones are becoming more powerful, and multitasking on these devices is becoming more common. Being able to switch between applications quickly and accurately is essential to efficient performance on these devices. This study examines how different multitasking interfaces on a touchscreen mobile device (LG Nexus 5) affect performance time and accuracy when switching between open applications. Sixteen participants performed sets of tasks that involved varying levels of complexity when switching between applications on two different multitasking interfaces (stacked and non-stacked). They were monitored for speed and error rates. Results show that a stacked multitasking interface allows for slightly faster application switching as well as fewer errors when switching than with a non-stacked multitasking interface. This paper concludes with a discussion of our results, limitations to the study, and ideas for future research.

@@

A stacked interface may only provide nominal speed and accuracy increases when compared to a non-stacked interface. As a result, future research should focus on alternate means to facilitate app switching as opposed to the conventional chronological list of applications. Throughout all mobile multitasking interfaces, almost exclusively, the "most recently used" rule is used to display applications in the list. Future research could look into using different sorting schemes to predict which application a user will need next. Perhaps machine learning could be applied to predict what application may be used next as is being tested in Apple?s new recents menu.
